### 2022-11-20 ms.rmd
Starting to add in the models. Going to use metafor so that I can make plots faster ;)

### *Do terrestrial and aquatic ectotherms differ in their capacity to acclimate?*
### *Does climate variability predict acclimation capacity among aquatic and terrestrial ectotherms?*
### *Does between-individual variation in acclimation capacities differ across terrestrial and aquatic ectotherms?*

>>>>

### *Do terrestrial and aquatic ectotherms differ in their capacity to acclimate?*

```{r acclimation_cap}
########################
### Differences in acclimation capacity between terrestrial, aquatic and marine
########################
phylo_cor <- vcv(tree_p0.7, cor = TRUE)
## lnRR first
lnRRQ10_data <- data_long %>% filter(grepl("lnRR", name)) %>% mutate(spp = species_full)

model1.1 <- metafor::rma.mv(effect_size, V = V, 
                            random = list(~1 + type | record_num,
                                            ~1 | species_full,
                                            ~1 | spp,
                                            ~1 | obs),
                            R = list(species_full = phylo_cor), dfs = "contain", test = "t", data = lnRRQ10_data)

### *Does climate variability predict acclimation capacity among aquatic and terrestrial ectotherms?*
### *Does between-individual variation in acclimation capacities differ across terrestrial and aquatic ectotherms?*
